%----------------------------------------------------------------------------------------
%	PACKAGES AND CONFIGURATION
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper]{article}

\usepackage[left=0.4in,right=0.4in,top=0.3in,bottom=0.3in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{helvet} % Use Helvetica (similar to Arial)

% Set main font to Helvetica (sans-serif)
\renewcommand{\familydefault}{\sfdefault}

% Remove page numbers
\pagenumbering{gobble}

% Color definitions
\definecolor{primaryblue}{RGB}{41, 98, 255}
\definecolor{accentpurple}{RGB}{41, 98, 255}
\definecolor{darkgray}{RGB}{64, 64, 64}
\definecolor{lightgray}{RGB}{128, 128, 128}

% Hyperlink setup with modern colors
\hypersetup{
	colorlinks=true,
	linkcolor=primaryblue,
	urlcolor=primaryblue,
	citecolor=primaryblue,
	pdftitle={Anas Ghareib - Resume},
	pdfauthor={Anas Ghareib},
	pdfsubject={Mobile Application Developer Resume},
	pdfkeywords={Flutter, Dart, React Native, Kotlin, Mobile Development}
}

% Enhanced section command with modern styling
\newcommand{\cvsection}[1]{%
	\vspace{4pt}%
	{\fontsize{10}{11}\selectfont\bfseries\color{darkgray}\uppercase{#1}}\\[1pt]%
	{\color{primaryblue}\rule{\linewidth}{1pt}}%
	\vspace{2pt}%
}

% Reduce list spacing and customize
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt, partopsep=0pt, leftmargin=*, label=\textcolor{primaryblue}{\raisebox{0.2ex}{\tiny$\bullet$}}}

% Font sizes optimized for one page
\renewcommand{\normalsize}{\fontsize{9.5}{11}\selectfont}
\renewcommand{\small}{\fontsize{9}{10.5}\selectfont}
\renewcommand{\large}{\fontsize{12}{14}\selectfont}

% Project title command with URL styling
\newcommand{\project}[2]{%
	\textbf{\href{#2}{\color{accentpurple}#1}}%
}

% Compact itemize for experience
\newenvironment{compactitemize}
{\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, leftmargin=*]}
	{\end{itemize}}

%----------------------------------------------------------------------------------------

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	HEADER
	%----------------------------------------------------------------------------------------
	
	{\large\bfseries\color{darkgray} ANAS GHAREIB}\\[1pt]
	{\normalsize\color{darkgray} Mobile Application Developer}\\[1pt]
	{\normalsize\color{darkgray} \href{https://ansgrb.github.io}{Website} \\ [2pt]
	{\small 
		\href{tel:+201121360922}{+201121360922} $\mid$ 
		\href{mailto:ansgrb@gmail.com}{\color{accentpurple}ansgrb@gmail.com} $\mid$ 
		\href{https://linkedin.com/in/ansgrb}{\color{accentpurple}linkedin.com/in/ansgrb} $\mid$
		\href{https://github.com/ansgrb}{github.com/ansgrb}
	}
	
	\vspace{6pt}
	
	%----------------------------------------------------------------------------------------
	%	TWO COLUMN LAYOUT
	%----------------------------------------------------------------------------------------
	
	\begin{minipage}[t]{0.3\textwidth}
		
		%----------------------------------------------------------------------------------------
		%	LEFT COLUMN - SUMMARY
		%----------------------------------------------------------------------------------------
		
		\cvsection{Summary}
		
		{\color{darkgray}
			Mobile software engineer with 4+ years of experience leading cross-platform development initiatives. Expert in Flutter ecosystem including Dart, Bloc/Riverpod, clean architecture, and performance optimization. Delivered 3 published applications (avg. 4.5/5 rating) with increasing focus on Flutter architecture and best practices. Proven ability to architect scalable mobile solutions from concept to production.
		}
		
		\vspace{4pt}
		
		%----------------------------------------------------------------------------------------
		%	CERTIFICATION
		%----------------------------------------------------------------------------------------
		
		\cvsection{Certification}
		

			\textbf{Linux Server Management and Security} 
			\href{https://www.coursera.org/account/accomplishments/verify/K4VWY2NW6BNJ}{[Credential]} \\
				{\color{lightgray}Coursera, Jul 2019}

				\vspace{2pt}

			\textbf{Python Specialization} 
				\href{https://www.coursera.org/account/accomplishments/specialization/certificate/6LCPBXXFRVJS}{[Credential]} \\
					{\color{lightgray}Coursera, Apr 2020}

				\vspace{4pt}
		
		%----------------------------------------------------------------------------------------
		%	KEY ACHIEVEMENTS
		%----------------------------------------------------------------------------------------
		
		\cvsection{Key Achievements}
		
		\textbf{App Publication}\\
		Published three Android apps with 4.5/5 average rating on Google Play
		
		\vspace{6pt}
		
		%----------------------------------------------------------------------------------------
		%	SKILLS
		%----------------------------------------------------------------------------------------
		
		\cvsection{Skills}
		
		{\color{darkgray}\fontsize{9}{10.5}\selectfont
			Flutter $\bullet$ Dart $\bullet$ Bloc/Cubit $\bullet$ Riverpod $\bullet$ Clean Architecture $\bullet$ Domain-Driven Design $\bullet$ React Native $\bullet$ Kotlin $\bullet$ Jetpack Compose $\bullet$ Swift $\bullet$ SwiftUI $\bullet$ MVVM $\bullet$ Provider $\bullet$ Redux $\bullet$ Google Firebase $\bullet$ Dart Frog $\bullet$ Node.js $\bullet$ NestJS $\bullet$ TypeScript $\bullet$ JavaScript ES6 $\bullet$ Python $\bullet$ SpringBoot $\bullet$ GraphQL $\bullet$ REST API $\bullet$ MongoDB $\bullet$ PostgreSQL $\bullet$ Supabase $\bullet$ AppWrite $\bullet$ Cloud Firestore $\bullet$ GCP $\bullet$ AWS Amplify $\bullet$ Cloudflare $\bullet$ Git $\bullet$ GitHub Actions $\bullet$ Codemagic $\bullet$ Fastlane $\bullet$ Docker $\bullet$ Gradle $\bullet$ Very Good CLI $\bullet$ Unit/Widget/Integration Testing $\bullet$ Golden Tests $\bullet$ Performance Profiling $\bullet$ Dart Code Metrics $\bullet$ Mockito $\bullet$ Dart FFI $\bullet$ Platform Channels $\bullet$ Freezed $\bullet$ BuildRunner $\bullet$ Flutter Flame $\bullet$ Visual Studio Code $\bullet$ Android Studio $\bullet$ IntelliJ IDEA $\bullet$ Figma $\bullet$ Dart DevTools $\bullet$ Linux Server $\bullet$ Blockchain development $\bullet$ Web3.0 integration $\bullet$ Solidity $\bullet$ Hardhat
		}
		
		\vspace{6pt}
		
		%----------------------------------------------------------------------------------------
		%	EDUCATION
		%----------------------------------------------------------------------------------------
		
		\cvsection{Education}
		
		\textbf{B.Sc. in Information Technology}\\
		Misr University for Science and Technology - MUST\\
		{\color{lightgray}09/2018 - 06/2023 \textit{Giza, Egypt}}
		
		\vspace{4pt}
		
		\textbf{Bachelor of Informatics (Credits)}\\
		Nile University\\
		{\color{lightgray}09/2017 - 06/2018 \textit{Giza, Egypt}}
		
		\vspace{4pt}
		
		\textbf{General Secondary Education, Science Track}\\
		Ohoud Secondary School\\
		{\color{lightgray}Class of 2017 \textit{Medinah, Saudi Arabia}}
		
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.68\textwidth}
		
		%----------------------------------------------------------------------------------------
		%	RIGHT COLUMN - EXPERIENCE
		%----------------------------------------------------------------------------------------
		
		\cvsection{Experience}
		
		\textbf{Mobile Application Developer}\\
		\textit{Leap Tech Kw}\\
		{\color{lightgray}01/2025 - 10/2025}
		{\color{lightgray} 	\textit{Full-time}}
		
		\vspace{1pt}
		
		
		\begin{compactitemize}
			\item Technical lead for Flutter development serving commercial and government applications serving thousands of daily active users.
			\item Implemented scalable Flutter architecture with Riverpod, dependency injection, and domain-driven design.
			\item Delivered high-performance mobile experiences with custom animations, responsive layouts, and offline capabilities.
			\item Integrated with enterprise backend systems including payment processing, real-time data, and analytics.
			\item Managed full development lifecycle from Dart codebase to app store deployment across multiple platforms.
		\end{compactitemize}
		
		\vspace{4pt}
		
		\textbf{Mobile Application Developer}\\
		\textit{CS Club Systems}\\
		{\color{lightgray}10/2020 - 01/2024}
		{\color{lightgray} 	\textit{Full-time}}
		
		\vspace{1pt}
		
		\begin{compactitemize}
			\item  Led the development of three apps (Dr. Zone, Club Systems, CS Computer Shop), achieving 4.5/5 ratings.
			\item Used Kotlin, Jetpack Compose libraries, Firebase, and MVVM to ensure scalable, maintainable apps
			\item Optimized performance and delivered clean UI with Jetpack Compose and robust REST integrations
		\end{compactitemize}
		
		\vspace{4pt}
		
		\textbf{System Administrator}\\
		\textit{Cairo Foam}\\
		{\color{lightgray}01/2019 - 03/2020}
		{\color{lightgray} 	\textit{Full-time, Contract}}
		
		\vspace{1pt}
		
		
		\begin{compactitemize}
			\item Hired following a critical data breach to rebuild and secure the company’s IT infrastructure. Led the design and implementation of a new internal network, connected and configured all workstations and devices, and established a robust backup and disaster recovery system to prevent future incidents. Ensured data integrity, improved system reliability, and enhanced overall cybersecurity posture.
		\end{compactitemize}
		
		\vspace{6pt}
		
		%----------------------------------------------------------------------------------------
		%	PROJECTS
		%----------------------------------------------------------------------------------------
		
		\cvsection{Projects}
	
		\project{Muhafthat}{https://ansgrb.github.io/muhafthatlandingpage/}\\
		A hyper-local community app connecting users within Kuwait's governorates for local news, events, and services.
		
		\vspace{2pt}
		
		\project{SpeedRa}{https://ansgrb.github.io/speedralandingpage/}\\
		A beautifully designed Flutter speed test app showcasing clean, scalable architecture for measuring internet performance.
		
		\vspace{2pt}
		
		\project{Rolex Boutique Template}{https://ansgrb.github.io/rolexboutiquelandingpage/}\\
		A scalable Flutter e-commerce template demonstrating practical Clean Architecture implementation.
		
		\vspace{2pt}
		
		\project{Dr. Zone}{https://ansgrb.github.io/drzonelandingpage/index.html}\\
		An all-in-one platform for patients to find top-rated doctors, book appointments, and manage health records.
		
		\vspace{2pt}
		
		\project{Dimension35c}{https://ansgrb.github.io/dimension35clandingpage/}\\
		A multiverse explorer app for diving into the characters, episodes, and locations of the Rick and Morty universe.
		
		
		\vspace{2pt}
		
		\project{Sabah Al Salem}{https://ansgrb.github.io/sabahalsalemlandingpage/}\\
		A comprehensive UX redesign proposal and interactive prototype to enhance the experience for customers and stakeholders.
		
		\vspace{2pt}
		
		\project{6 October Club}{https://ansgrb.github.io/6oclandingpage/}\\
		A comprehensive mobile app design proposal to redefine the member experience through a modern, feature-rich digital platform.
		
		
		\vspace{2pt}
		
		\project{iconsync}{https://github.com/ansgrb/iconsync}\\
		A Gradle plugin that automates launcher icon synchronization from Android to iOS in Kotlin Multiplatform projects.
			
		
	\end{minipage}
	
\end{document}